WORKING TITLE: The adaptive value of green nest material across birds: A systematic review and meta-analysis

### 2025-02-17 manuscript_GNM.qmd
Added supplementary material and a structure that should work in principle

@dimri2024

then methods and results (generally following one of my previous meta-analysis, e.g. the Gambusia one)

@@

>>>>

### Registration and Reporting

We pre-registered our predictions, methods and planned analysis prior to data exploration and analysis [@dimri2024]. We followed the PRISMA-EcoEvo guidelines [@odea2021] for reporting this study (in @supptbl-1). All resources associated with this study, including data and code, are available at [https://github.com/shreyadimri/Green_Nest_Material](#0){.uri} (insert Zenodo citation later).

### Systematic Review

#### Literature search

We conducted a systematic search on Web of science Core Collection and Scopus citation database on 07.09.2022 @supptbl-2

#### Eligibility criteria

#### Study selection and eligibility criteria

-   Keyword search: where and when..

-   Justification for development of keyword search

-   Findings/Results of search

-   Exclusion criteria

-   How many papers in final meta-analysis and how many effect sizes

-   PRISMA Diagram link

### Data Extraction

-   What did we extract in priority order

-   Wrote to authors for missing info, used methods to deal with missing info

-   Figures extraction

-   Moderators extracted

### Effect size calculation

### Meta-analysis and meta-regressions

-   main effect model

-   meta-regressions for testing hypothesis

-   meta-regressions for exploratory analyses

Senstivity analysis and Publication Bias Test

### Deviations from registration

@@

<details><summary> Supplementary materials </summary>
{{< include supplementary_appendix.qmd >}}
</details>
